Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
Updates from Overleaf

>>>>

Across 78 countries in this study, the data provides 28 numerical variables and four descriptive variables. Majority of the data is from 2010 - 2020 (Figure 1). Therefore, we can analyze the global condition of water accessibility by utilizing the most up to date surveys. Most of the variables are related to water accessibility by their locations, time, and water resources. This also allows us to find water accessibility predictor variables and new clustering graphs.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}
\subsection*{Model results}
First, we developed a correlation chart to quickly analyze if there is any great correlation between all the 28 numerical variables that may pertain to water accessibility.

begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{year}
  \caption{Distribution of years of water accessibility variables}
  \label{fig:year}
\end{figure}
